Urban Heat Risk Mapping Using Multiple Point Patterns in Houston, Texas

### 2016-12-13 reviewer_response.tex

\documentclass{article}
\usepackage[letterpaper,margin=1in]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsbsy}
\usepackage{epsfig}
\usepackage{color}
\usepackage{url}
\usepackage{dsfont}
\usepackage{bm}
\usepackage{csquotes}

\begin{document}
\begin{center}{\large \textsc{Response to Comments From Reviewer 1}}\end{center}
\begin{enumerate}
  \item \textit{I really feel given the nature of this paper (it is not the definitive guide to heat and health in Houston) that it needs to be fully capable of reproducibility.   I therefore don't feel the part of the algorithm set out in section 2.4 is sufficient.   For example I had to read to find details for $\boldsymbol{\alpha}_p$ etc., some of the other comments (the posterior is fully known) were a little glib.   I think the entire sampler could be set out in the text, but if not an appendix could be used. Links to code would also be helpful (I appreciate there are confidentiality issues with some of the data).}

We strongly welcome comments to make our work more reproducible. We rearranged the paper to put all of the information relevant to the algorithm in 2.4 together in the same section, making it easier to find details about how the model was fit. In Section 2.3 we explicitly detailed which parameters had conjugate priors and made sure to reference this section when discussing the algorithm. We also wrote out the complete conditional distributions for those parameters which belong to a known family of distributions in equations (9), (10) and (11) in an effort to clarify what was meant by our comments such as ``the posterior is fully known.'' Finally, the code used to fit the model can be found here: \textcolor{red}{\textit{Link to github repository}}.

@@

\item\textit{I wasn't sure about claiming IG(2,1) or the Dirichlet prior were non-informative.   Using population counts sounds very informative (or was it the expected values that were used).}

In response to this comment we added a significant amount of justification in Section 2.3 detailing exactly why these priors are non-informative. Additionally, we clarified our comments in order to avoid the miscommunication that we were using population counts in our prior. The population counts only come into play through the data in the likelihood.

\item\textit{It would be useful to understand some of the covariate posterior information; does the 0.51 versus 0.49 for males versus females really mean anything? This might be a great parameter to set out the trace plots and density plots which would help provide information on convergence as well as understanding the relevance of what sounds like a modest difference to me.}

We have done two things to address this comment: First, we provided highest posterior density (HPD) intervals for the probabilities in Table 4, showing that there is no overlap for the male and female mortality probabilities and suggesting that the difference is statistically significant. We feel that in terms of understanding uncertainty this interval is a more useful summary than trace plots, and that a density plot does not add enough additional information beyond the HPD interval to justify its inclusion. Second, in order to provide additional context for this difference we have included density plots for the $\delta$ parameters for the 911 calls and mortalities. Recall that $\delta$ represents the expected total number of incidents for each health outcome across the spatial region. Multiplying this number ($\approx 15228$ for mortalities) by the probabilities associated with each sex gives an estimate for the size of the difference (i.e., about $7766$ incidents of male mortality vs $7461$ for females). Recognizing that this small difference in probabilities represents around 300 deaths suggests that this effect is practically significant as well, though not to the degree of some other factors, such as race/ethnicity.

@@

% \textcolor{blue}{Yeah - what s/he wants is not actually trace plots but measures of uncertainty.  For example, of 0.49 statistically different from 0.51 (i.e.\ do credible intervals overlap)?  For the numbers you cite on page 22, can you just include some form of interval to express uncertainty?}

\item\textit{Why do a spatial misalignment (Brunsdon and Comber)?   There are comparable numbers of census tracts and grid squares; using census tracts directly sounds like a tractable GIS problem (the denominator is the area of the census tract, points-in-polygons can count the necessary points).   I couldn't see anything in the mathematics of the intensity that would prevent the census tracts being used, and you remove a layer of approximation.}

We responded to this comment by adding the following text to the article:

\begin{displayquote}
A potential solution to avoid realigning the census data to the grid cells is to let the census block groups equal the $\mathcal{G}_k$ denoted in (2) rather than the grid cells. However, the heat information used in this research (described in detail in Section 3.1) is provided at a 1-km$^2$ resolution and these grid cells were chosen to align exactly with the available heat data. Using the block groups in place of the grid cells would necessitate aligning the heat information to the census block group areas. Because heat is our primary variable of interest we prefer realigning the demographic information to the grid associated with the heat data as opposed to the alternative. Therefore, we proceed having aligned the population data as described.
\end{displayquote}

\item\textit{Heat enters as an upper level covariate, with ecological fallacy risks?   Are the census data not available to study how some of these features vary with key other demographics?   I appreciate all the census data are disclosure limited but some multiway information on air conditining and age band could really limit the potential problems with confounders in the aggregate analysis.}

@@

In order to address this concern, we examined the impact of additional demographic covariates from the census data on our model. We also included all two-way interaction terms between the various covariates as potential predictors in our model in order to mitigate the potential problems with confounders (see Table X), as suggested by the reviewer.

\textcolor{red}{Jacob: I am not sure I follow the Table 2 in the paper comparing all the different models.  Did each of these models have the same DIC?}

\item\textit{Although you make a comment in the end about the lack of suitable model fit diagnostics there is a lot more that is already available.   WAIC / Gneiting and Tillmans's proper scoring rules seem appropriate given a major outcome is a risk map.}

The comment in our article was not about model fit diagnostics that allow you to compare different models, but rather about diagnostics that are an objective measure of how well the chosen model fits the data. Neither Tillman Gneiting's proper scoring rules or WAIC provide a solution to this particular problem. For example, continuous rank probability scores are to assess the predictive ability of a model rather than the fit of a model to available data. Additionally, Gelman et. al. (2014; \textit{Statistics and Computing}) argue that ``a cost of using WAIC is that it relies on a partition of the data into $n$ pieces, which is not so easy to do in some structured-data settings such as time series, spatial, and network data'' and suggest that this makes WAIC an inappropriate measure for the type of spatial model we use in this paper. \textcolor{red}{I had originally intended to implement some of the posterior predictive checking from the Leininger paper, but I feel like we're running out of time. Do you think we can get by without it?}

@@

An additional implicit assumption with (5) is the independence assumption among the log relative risks for each health outcome given the overall, ``cumulative'' log relative risk surface $\boldsymbol{\mu}$. For the application considered here this assumption is likely to, approximately, hold because the time frame for the 911 call data is 2006-2010 while the time frame for the mortality data is 1999-2006 (a minimal overlap); however, in other applications independence may not hold. In such cases, a multivariate spatial model (see Genton and Kleiber (2015) for a discussion) could be used in place of (5). We note the possible benefit of modeling dependence between the log relative risks but we do not explore this option here.
\end{displayquote}

\item\textit{The prior assumptions and choices need to be justified especially for those non-informative and vague priors. Also, "Because the priors for $\alpha_p, \gamma_p$" etc., "are all conjugate, their posterior distributions are known..." is not clear to me that the claim is valid. It would also be helpful if the results from the MCMC are presented so to confirm convergence.}

We added additional detail justifying our prior assumptions and also explicitly demonstrated the conjugacy of the Dirichlet prior in Section 2.3. Because we have so many parameters, we prefer not to include trace plots in the paper, but we have attached them to this document and can add them in the supplementary materials for the paper if desired.

### 2016-12-13 jrssc-mpp.tex
Responded to almost all of the reviewer comments; just need final results to update a few numbers and then we're done.

\begin{abstract}
Extreme heat, or persistently high temperatures in the form of heat waves,
adversely impact human health. To study such effects, risk maps are a common
epidemiological tool used to identify regions and populations that are
more susceptible to these negative outcomes; however, the negative health 
effects of high temperatures are manifested differently among
different segments of the population. In this paper, we propose a novel,
hierarchical marked point process model that merges multiple health outcomes
into an overall heat risk map. Specifically, we consider health outcomes of  heat stress-related 911 calls and mortalities across the city of Houston, Texas. We show that combining multiple health outcomes leads to a broader
understanding of the spatial distribution of heat risk than a single 
health outcome.
\end{abstract}
\keywords{Poisson point processes, risk mapping}

@@

Additionally, at the process layer of the model we assume 
\begin{align}
\boldsymbol{\mu} \sim \mathcal{N}(\mathbf{X}\boldsymbol{\beta},\sigma^2_\mu\mathbf{M}_\mu)
\label{mu}
\end{align}
where $\mathbf{X}$ is a $K\times Q$ design matrix of covariates with associated coefficients 
$\boldsymbol{\beta}$, $\sigma^2_\mu$ is a variance and $\mathbf{M}_\mu$ is a spatial correlation 
matrix implied by the Mat\'{e}rn correlation function with smoothness $\nu_\mu$ and 
decay $\psi_\mu$. The regression in \eqref{mu} allows us to assess if covariates such as 
poverty, age, or urban temperature affect the height of the global intensity surface 
through inference on the parameters $\boldsymbol{\beta}$.

@@

\textcolor{red}{Our approach for the remaining unknown parameters is to assume vague priors (and conjugate 
where possible). %Is the following sentence sufficient to explain why we use vague priors?
This is justified because there is sufficient data to learn these parameters without the need to rely heavily on prior information. For $\delta_p$, we assume $\delta_p \sim \mathcal{G}(0.001, 0.001)$, where $\mathcal{G}(a,b)$ denotes the gamma distribution with shape $a$ and rate $b$. Note that for $\delta_p$ the likelihood in \eqref{likelihood} is proportional to $$\exp\left(-\delta_p\right)\delta_p^{n_p},$$ the kernel of a Poisson distribution. Therefore, the gamma prior for $\delta_p$ is conjugate, producing a posterior distribution of $\mathcal{G}(n_p + 0.001, 1 + 0.001)$. We assume $\{\sigma^2_p\}$ and $\sigma^2_\mu$ are independent 
$\mathcal{IG}\left(2.001, 1.001\right)$ 
random variables where $\mathcal{IG}(a,b)$ denotes the inverse-gamma distribution with scale 
$a$ and rate $b$, a well-known conjugate prior for normal variance parameters. The $\mathcal{IG}(2.001, 1.001)$ distribution has a variance of 1000, providing sufficient flexibility for the data to accurately dictate the variances. For the regression coefficients we assume that $\boldsymbol{\beta} \sim 
\mathcal{N}(0, 50\mathbf{I}_{Q})$, leading to a Gaussian complete conditional for $\boldsymbol{\beta}$. 
Conjugate prior distributions for each spatial smoothness parameter (the $\nu$'s) and decay 
parameter (the $\psi$'s) are not available; however, following the results of \cite{Zhang2004}, 
a vague prior for the variance parameters (the $\sigma^2$'s) allows each smoothness and decay 
parameter to be fixed without loss generality or predictive power.}

\subsection{Model Fitting}
\begin{algorithm}
  Let $N$ be the number of MCMC draws, large enough that convergence is attained.
  \BlankLine
  \For{$p$ in $1:P$}{
  Sample $N$ draws from $\delta_{p} \sim \mathcal{G}(n_p + 0.001, 1.001)$\;
  Sample $N$ draws from $\boldsymbol\alpha_p \sim \text{Dir}\left(n_{p,0}+1, n_{p,1}+1, \dots, n_{p,113} + 1\right)$\;
  Sample $N$ draws from $\boldsymbol\gamma_p \sim \text{Dir}\left(n_{p,\text{Female}} + 1, n_{p,\text{Male}} + 1\right)$\;
  Sample $N$ draws from $\boldsymbol\xi_p \sim \text{Dir}\left(n_{p,\text{Asian}} + 1, \dots, n_{p,\text{White}}\right)$\;
  }
  \For{$i$ in $1:N$}{
    \For{$p$ in $1:P$} {
      Sample $\sigma^2_p \sim \left[ \sigma^2_p | \boldsymbol{\phi}^\star_p, \mathbf{M}_p\right]$\label{draws2}\;
      Sample $\boldsymbol\phi^\star_p \sim \left[ \boldsymbol\phi^\star_p | \sigma^2_p, \mathbf{M}_p \right]$\label{drawphi}\;
    }
    Sample $\sigma^2_\mu \sim \left[ \sigma^2_\mu | \boldsymbol{\mu}, \boldsymbol{\beta}, \mathbf{M}_\mu \right]$\label{drawsmu}\;
    Sample $\boldsymbol{\mu} \sim \left[ \boldsymbol{\mu} | \{\boldsymbol{\phi}^\star_p\}, 
    \{\sigma^2_p\}, \{\mathbf{M}_p\}, \sigma^2_\mu, \mathbf{M}_\mu, \boldsymbol{\beta} \right]$\label{drawmu}\;
    Sample $\boldsymbol{\beta} \sim \left[ \boldsymbol{\beta} | \boldsymbol{\mu}, \sigma^2_\mu, \mathbf{M}_\mu \right]$\label{drawbeta}\;
  }
  \caption{Model fitting algorithm. \label{algo:model_fit}}

\end{algorithm}
\textcolor{red}{We fit this model within a Bayesian framework, using the Markov Chain Monte Carlo (MCMC) algorithm outlined in Algorithm \ref{algo:model_fit}. Notice that because the parameters on lines 2-7 all have conjugate priors (as described in Section \ref{sec:hyperprior}), their posterior densities are completely known and all $N$ draws can be taken simultaneously. Recall that $n_{p,0}$ denotes the number of people who experienced health outcome $p$ at age $0$, $n_{p,Female}$ indicates the number of females who experienced health outcome $p$, and so on. }

@@

\textcolor{red}{Using a sampler of this design, 10000 draws were taken from the posterior distributions for each of these parameters, after a burn-in of 10000.\footnote{R code used to implement this algorithm is provided in the supplementary materials.} In order to assess convergence, we examined traceplots for each of the parameters and used Monte Carlo standard error (MCSE). \cite{Jones2006} calculate MCSE by dividing the chains into batches and using each batch mean to calculate variance between batches. Small MCSE values occur only when the variance between batches is low (i.e., each batch is approximately equal), thereby providing evidence of convergence. We calculated MCSE using the \texttt{mcmcse} package in R \citep{Flegal2015}, and the largest MCSE value for all of our parameters was XXXXX. Based on these MCSE values and visual inspection of the traceplots, we are satisfied that convergence was attained.}

@@

We fit the model in Section \ref{model} using each of these temperature variables (one at a time) and then calculated the deviance information criterion (DIC) \citep{Spiegelhalter2002} as a measure of model fit. 
Table \ref{DIC} 
shows that the model produced the lowest DIC value when fit with max HI so the numerical estimates and risk maps shown in this chapter are from the model fit with this temperature measurement. Figure \ref{fig:temp} displays the average maximum HI values associated with each grid cell and shows a clear spatial distribution, with higher temperatures concentrated near the city center. Note that the DIC values in Table \ref{DIC} 
are all very close, indicating little difference in model fit between the different variables.  This is, perhaps, due to the fact that the covariates enter our model at the mean intensity surface layer (in the regression for $\boldsymbol{\mu}$) at which point it is difficult to distinguish between the different heat variables. That is, because $\boldsymbol{\mu}$ captures both the 911 calls and mortalities, it is possible that any of the measured heat variables explain the combined impact of heat on ``health'' whereas specific heat variables better explain specific health outcomes.

\textcolor{red}{Recall that in \eqref{mu} $\boldsymbol{\mu}$ can be regressed on covariates $\mathbf{X}$ in order to account for potential confounding effects. For all models that we considered $\mathbf{X}$ included an intercept term and temperature data detailed above. Table \ref{tab:model_comparison} shows which additional demographic variables were included in $\mathbf{X}$ as well as indicating whether or not two-way interaction terms were also included in each model. The DIC in the final column of the table indicates that Model X provides the best fit for the data, and so the rest of this paper refers to this model. The percentage of people without air conditioning was taken from the Harris County tax assessor parcel database while all remaining covariates were taken from 2000 U.S. Census Data. Both data sources were aligned with our discrete grid using the method described in Section \ref{likelayer}. }

% Table created by stargazer v.5.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Tue, Nov 03, 2015 - 15:11:28
\begin{table}
  \caption{DIC values for models fit with different temperature measurements.} 
  \label{DIC} 
\begin{tabular}{@{\extracolsep{5pt}} cc} 
\\[-1.8ex]\hline
\hline \\[-1.8ex]  
Temperature Measurement & DIC \\
\hline \\[-1.8ex]  
HI Max & $220474$ \\ 
HI Min & $221016$ \\ 
T2 Max & $220998$ \\ 
T2 Min & $220999$ \\ 
SWBG Max & $221008$ \\ 
SWBG Min & $221021$ \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

\begin{table}
  \caption{In order to control for potential confounding effects, we compared 15 different models that included a variety of demographic variables and two-way interactions. The variables included in each model and whether or not interaction terms were considered is indicated in the table below. We also include DIC in order to compare models and select the one that provides the best fit.}
  \label{tab:model_comparison}

  \begin{tabular}{@{\extracolsep{5pt}} lccccccccc|c}
  \\[-1.8ex]\hline
  \hline \\[-1.8ex]
  & \multicolumn{9}{c}{Variables} & \\
  & \rot{\% over 65} & \rot{\% under 5} & \rot{\% Black} & \rot{\% Hispanic} & \rot{\% w/o AC} & \rot{\% disabled} & \rot{\% living alone} & \rot{\% in poverty} & \rot{Interactions} & DIC \\\hline
  Model 01 &   &   &   &   &   &   &   &   &   & 12345 \\
  Model 02 & X & X &   &   &   &   &   &   &   & 12345 \\
  Model 03 &   &   & X & X &   &   &   &   &   & 220523 \\
  Model 04 &   &   &   &   & X & X & X & X &   & 220482 \\
  Model 05 & X & X & X & X &   &   &   &   &   & 220526 \\
  Model 06 & X & X &   &   & X & X & X & X &   & 220512 \\
  Model 07 &   &   & X & X & X & X & X & X &   & 220497 \\
  Model 08 & X & X & X & X & X & X & X & X &   & 220498 \\
  Model 09 & X & X &   &   &   &   &   &   & X & 220529 \\
  Model 10 &   &   & X & X &   &   &   &   & X & 220455 \\
  Model 11 &   &   &   &   & X & X & X & X & X & 220493 \\
  Model 12 & X & X & X & X &   &   &   &   & X & 220522 \\
  Model 13 & X & X &   &   & X & X & X & X & X & 12345 \\
  Model 14 &   &   & X & X & X & X & X & X & X & 12345 \\
  Model 15 & X & X & X & X & X & X & X & X & X & 12345 \\
  \hline\\[-1.8ex]
  \end{tabular}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.7\textwidth]{imgs/avg_temp.pdf}
  \caption{Maximum NWS Heat Index in Houston, averaged over the summer months of 1999 -- 2010. Notice that there is a clear concentration of higher temperatures in the center of the city.}
  \label{fig:temp}
\end{figure}

\subsection{Risk Maps}
The maps in Figure \ref{relative_risks} show the posterior estimates for $\boldsymbol\phi^\star_{p}$ where $p\in \{911,\text{Mort}\}$, the log relative risks for each health outcome, and $\boldsymbol\mu$, the vector of log relative risks averaged across all health outcomes. Notice that in Figure \ref{relative_risks}a, the map showing $\boldsymbol\phi^\star_{911}$, the majority of the high risk area is concentrated in the city center. This is in line with the temperature measurements depicted in Figure \ref{fig:temp}, which shows a concentration of higher temperatures in the middle of Houston. Additionally, the area of highest concentration occurs in a downtown location with several parks and other walkable destinations, which may be a potential explanation for why heat-related 911 calls occur with relatively high frequency in this area.

There is a somewhat surprising area of extremely high relative risk for 911 calls in the northern part of the city; however, inspection of the underlying geography reveals that much of this area is covered by an airport, resulting in extremely low population levels (fewer than 25 people per square kilometer) yet a relatively large incidence of heat-related 911 calls (4, 6, and 7 phone calls in each of the three affected grid cells, respectively). Another important feature of the 911 call map is that the range for $\boldsymbol\phi^\star_{911}$ is much larger than the range for either $\boldsymbol\phi^\star_{\text{Mort}}$ or $\boldsymbol\mu$ and that far more of the $\boldsymbol\phi^\star_{911}$ values reach into the upper end of the distribution, with 7.4 percent of $\boldsymbol\phi^\star_{911}$ values greater than 1, compared to just 1.2 percent of the elements of $\boldsymbol\phi^\star_{\text{Mort}}$ greater than 1 and less than 1 percent of the elements of $\boldsymbol\mu$ greater than 1. This is likely due to sparsity of data: if more heat-related 911 calls were observed, the associated locations could potentially be more diffuse than those currently observed, leading to lower relative risk scores. Notice also that the credible interval widths (see Figure \ref{relative_risks}b), unsurprisingly, are largest where no 911 calls were observed and estimation of $\phi^\star_{911,k}$ was dependent entirely on spatial correlation.

>>>>

\begin{abstract}
Extreme heat, or persistently high temperatures in the form of heat waves,
adversely impacts human health. To study such effects, risk maps are a common
epidemiological tool used to identify regions and populations that are
more susceptible to these negative outcomes; however, the negative health 
effects of high temperatures are manifested differently among
different segments of the population. In this paper, we propose a novel,
hierarchical marked point process model that merges multiple health outcomes
into an overall heat risk map. Specifically, we consider health outcomes of  heat stress-related 911 calls and mortalities across the city of Houston, Texas. We show that combining multiple health outcomes leads to a broader
understanding of the spatial distribution of heat risk than a single 
health outcome.
\end{abstract}
\keywords{Poisson point processes, risk mapping}

@@

At the process layer of the model we also assume 
\begin{align}
\boldsymbol{\mu} \sim \mathcal{N}(\mathbf{X}\boldsymbol{\beta},\sigma^2_\mu\mathbf{M}_\mu)
\label{mu}
\end{align}
where $\mathbf{X}$ is a $K\times Q$ design matrix of covariates with associated coefficients 
$\boldsymbol{\beta}$, $\sigma^2_\mu$ is a variance and $\mathbf{M}_\mu$ is a spatial correlation 
matrix implied by the Mat\'{e}rn correlation function with smoothness $\nu_\mu$ and 
decay $\psi_\mu$. The regression in \eqref{mu} allows us to assess if covariates such as 
poverty, age, or urban temperature affect the height of the global intensity surface 
through inference on the parameters $\boldsymbol{\beta}$.

@@

\textcolor{red}{Our approach for the remaining unknown parameters is to assume vague priors (and conjugate 
where possible). %Is the following sentence sufficient to explain why we use vague priors?
This is justified because there is sufficient data to learn these parameters without the need to rely heavily on prior information. For $\delta_p$, we assume $\delta_p \sim \mathcal{G}(0.001, 0.001)$, where $\mathcal{G}(a,b)$ denotes the gamma distribution with shape $a$ and rate $b$. Note that for $\delta_p$ the likelihood in \eqref{likelihood} is proportional to $$\exp\left(-\delta_p\right)\delta_p^{n_p},$$ the kernel of a Poisson distribution. Therefore, the gamma prior for $\delta_p$ is conjugate, producing a posterior distribution of $\mathcal{G}(n_p + 0.001, 1 + 0.001)$. We assume $\{\sigma^2_p\}$ and $\sigma^2_\mu$ are independent 
$\mathcal{IG}\left(2.001, 1.001\right)$ 
random variables where $\mathcal{IG}(a,b)$ denotes the inverse-gamma distribution with scale 
$a$ and rate $b$, a well-known conjugate prior for normal variance parameters. The $\mathcal{IG}(2.001, 1.001)$ distribution has a variance of 1000, providing sufficient flexibility for the data to accurately dictate the variances. For the regression coefficients we assume that $\boldsymbol{\beta} \sim 
\mathcal{N}(0, 50\mathbf{I}_{Q})$, which leads to a Gaussian complete conditional for $\boldsymbol{\beta}$. 
Conjugate prior distributions for each spatial smoothness parameter (the $\nu$'s) and decay 
parameter (the $\psi$'s) are not available; however, following the results of \cite{Zhang2004}, 
a vague prior for the variance parameters (the $\sigma^2$'s) allows each smoothness and decay 
parameter to be fixed without loss generality or predictive power.}

\subsection{Model Fitting}
\begin{algorithm}
  Let $N$ be the number of MCMC draws, large enough that convergence is attained.
  \BlankLine
  \For{$p$ in $1:P$}{
  Sample $N$ draws from $\delta_{p} \sim \mathcal{G}(n_p + 0.001, 1.001)$\;
  Sample $N$ draws from $\boldsymbol\alpha_p \sim \text{Dir}\left(n_{p,0}+1, n_{p,1}+1, \dots, n_{p,113} + 1\right)$\;
  Sample $N$ draws from $\boldsymbol\gamma_p \sim \text{Dir}\left(n_{p,\text{Female}} + 1, n_{p,\text{Male}} + 1\right)$\;
  Sample $N$ draws from $\boldsymbol\xi_p \sim \text{Dir}\left(n_{p,\text{Asian}} + 1, \dots, n_{p,\text{White}}\right)$\;
  }
  \For{$i$ in $1:N$}{
    \For{$p$ in $1:P$} {
      Sample $\sigma^2_p \sim \left[ \sigma^2_p | \boldsymbol{\phi}^\star_p, \mathbf{M}_p\right]$\label{draws2}\;
      Sample $\boldsymbol\phi^\star_p \sim \left[ \boldsymbol\phi^\star_p | \sigma^2_p, \mathbf{M}_p \right]$\label{drawphi}\;
    }
    Sample $\sigma^2_\mu \sim \left[ \sigma^2_\mu | \boldsymbol{\mu}, \boldsymbol{\beta}, \mathbf{M}_\mu \right]$\label{drawsmu}\;
    Sample $\boldsymbol{\mu} \sim \left[ \boldsymbol{\mu} | \{\boldsymbol{\phi}^\star_p\}, 
    \{\sigma^2_p\}, \{\mathbf{M}_p\}, \sigma^2_\mu, \mathbf{M}_\mu, \boldsymbol{\beta} \right]$\label{drawmu}\;
    Sample $\boldsymbol{\beta} \sim \left[ \boldsymbol{\beta} | \boldsymbol{\mu}, \sigma^2_\mu, \mathbf{M}_\mu \right]$\label{drawbeta}\;
  }
  \caption{Model fitting algorithm. \label{algo:model_fit}}
\end{algorithm}

\textcolor{red}{We fit this model within a Bayesian framework, using the Markov Chain Monte Carlo (MCMC) algorithm outlined in Algorithm \ref{algo:model_fit}. Notice that because the parameters on lines 2-7 all have conjugate priors (as described in Section \ref{sec:hyperprior}), their posterior densities are completely known and all $N$ draws can be taken simultaneously. Recall that $n_{p,0}$ denotes the number of people who experienced health outcome $p$ at age $0$, $n_{p,Female}$ indicates the number of females who experienced health outcome $p$, and so on. }

@@

\textcolor{red}{Using a sampler of this design, \textcolor{blue}{10000} draws were taken from the posterior distributions for each of these parameters, after a burn-in of \textcolor{blue}{10000.}\footnote{R code used to implement this algorithm is provided in the supplementary materials.} In order to assess convergence, we examined traceplots for each of the parameters and used Monte Carlo standard error (MCSE). \cite{Jones2006} calculate MCSE by dividing the chains into batches and using each batch mean to calculate variance between batches. Small MCSE values occur only when the variance between batches is low (i.e., each batch is approximately equal), thereby providing evidence of convergence. We calculated MCSE using the \texttt{mcmcse} package in R \citep{Flegal2015}, and the largest MCSE value for all of our parameters was \textcolor{blue}{XXXXX.} Based on these MCSE values and visual inspection of the traceplots, we are satisfied that convergence was attained.}

@@

We fit the model in Section \ref{model} using each of these temperature variables (one at a time) and then calculated the deviance information criterion (DIC) \citep{Spiegelhalter2002} as a measure of model fit. 
Table \ref{DIC} shows that the model produced the lowest DIC value when fit with min HI so the numerical estimates and risk maps shown in this chapter are from the model fit with this temperature measurement. Figure \ref{fig:temp} displays the average minimum HI values associated with each grid cell and shows a clear spatial distribution, with higher temperatures concentrated near the city center. 
% Note that the DIC values in Table \ref{DIC} 
% are all very close, indicating little difference in model fit between the different variables.  This is, perhaps, due to the fact that the covariates enter our model at the mean intensity surface layer (in the regression for $\boldsymbol{\mu}$) at which point it is difficult to distinguish between the different heat variables. That is, because $\boldsymbol{\mu}$ captures both the 911 calls and mortalities, it is possible that any of the measured heat variables explain the combined impact of heat on ``health'' whereas specific heat variables better explain specific health outcomes.

\textcolor{red}{Recall from \eqref{mu} that $\boldsymbol{\mu}$ can be regressed on covariates $\mathbf{X}$ in order to account for potential confounding effects. For all models that we considered $\mathbf{X}$ included an intercept term and the temperature data detailed above. Table \ref{tab:model_comparison} shows which additional demographic variables were included in $\mathbf{X}$ as well as indicating whether or not interactions with temperature were also considered. The potential confounding variables we examined were all characteristics of the grid cell and include the percentage of the population over 65 years old, percentage of the population under 5 years old, percentage of the population that is Black, percentage of the population that is Hispanic, percentage of the population without central air conditioning, and the percentage of residential buildings in the grid cell that are categorized as ``low,'' ``very low,'' or ``poor'' quality in the Harris County tax assessor parcel database. The percentage of people without air conditioning and percentage of low quality buildings were taken from the aforementioned Harris County database while all remaining covariates were taken from 2010 U.S. Census Data. Both data sources were aligned with our discrete grid using the method described in Section \ref{likelayer}. The DIC values listed in the final column of Table \ref{tab:model_comparison} indicate that \textcolor{blue}{Model X} provides the best fit for the data, and so the rest of this paper refers to this model.}

% % Table created by stargazer v.5.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% % Date and time: Tue, Nov 03, 2015 - 15:11:28
\begin{table}
  \caption{DIC values for models fit with different temperature measurements.} 
  \label{DIC} 
\begin{tabular}{@{\extracolsep{5pt}} cc} 
\\[-1.8ex]\hline
\hline \\[-1.8ex]  
Temperature Measurement & DIC \\
\hline \\[-1.8ex]  
HI Max & $220845$ \\ 
HI Min & $220733$ \\ 
T2 Max & $220823$ \\ 
T2 Min & $220830$ \\ 
SWBG Max & $220772$ \\ 
SWBG Min & $220825$ \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

% Table created by stargazer v.5.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Tue, Nov 03, 2015 - 15:11:28
% \begin{table}%\centering 
%   \caption{DIC Values for Models Fit Using Each Temperature Measurement.} 
%   \label{DIC} 
% \begin{tabular}{@{\extracolsep{5pt}} cc} 
% \\[-1.8ex]\hline
% \hline \\[-1.8ex]  
% Temperature Measurement & DIC \\
% \hline \\[-1.8ex]  
% HI Max & $221125$ \\ 
% HI Min & $221123$ \\ 
% T2 Max & $221155$ \\ 
% T2 Min & $221151$ \\ 
% SWBG Max & $221168$ \\ 
% SWBG Min & $221131$ \\ 
% \hline \\[-1.8ex] 
% \end{tabular} 
% \end{table}

\begin{table}
  \caption{In order to control for potential confounding effects, we compared 15 different models that included a variety of demographic variables and two-way interactions. All models included the temperature variable. The table below indicates which additional variables were included in each model and whether or not interaction with temperature was considered. For example, Model 09 includes temperature, percent over 65, percent under 5, and all two-way interactions with temperature. We also include DIC in order to compare models and select \textcolor{blue}{Model XX} as providing the best fit.}
  \label{tab:model_comparison}

  \begin{tabular}{@{\extracolsep{5pt}} lccccccc|c}
  \\[-1.8ex]\hline
  \hline \\[-1.8ex]
  & \multicolumn{7}{c}{Variables} & \\
  & \rot{\% over 65} & \rot{\% under 5} & \rot{\% Black} & \rot{\% Hispanic} & \rot{\% w/o AC} & \rot{\% Low Quality Buildings} & \rot{Interactions w/ Temperature} & DIC \\\hline
  Model 01 &   &   &   &   &   &   &   & 220733 \\
  Model 02 & X & X &   &   &   &   &   & 220699 \\
  Model 03 &   &   & X & X &   &   &   & 220796 \\
  Model 04 &   &   &   &   & X & X &   & 220763 \\
  Model 05 & X & X & X & X &   &   &   & 220741 \\
  Model 06 & X & X &   &   & X & X &   & 220809 \\
  Model 07 &   &   & X & X & X & X &   & 220787 \\
  Model 08 & X & X & X & X & X & X &   & 220793 \\
  Model 09 & X & X &   &   &   &   & X & 220788 \\
  Model 10 &   &   & X & X &   &   & X & 220814 \\
  Model 11 &   &   &   &   & X & X & X & 220771 \\
  Model 12 & X & X & X & X &   &   & X & 220822 \\
  Model 13 & X & X &   &   & X & X & X & 220865 \\
  Model 14 &   &   & X & X & X & X & X & 220812 \\
  Model 15 & X & X & X & X & X & X & X & 220872 \\
  \hline\\[-1.8ex]
  \end{tabular}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.7\textwidth]{imgs/avg_himin.pdf}
  \caption{Minimum NWS Heat Index in Houston, averaged over the summer months of 1999 -- 2010. Notice that there is a clear concentration of higher temperatures in the center of the city.}
  \label{fig:temp}
\end{figure}

\subsection{Risk Maps}
The maps in Figure \ref{relative_risks} show the posterior estimates for $\boldsymbol\phi^\star_{p}$, the log relative risks for each health outcome, where $p\in \{911,\text{Mort}\}$, and $\boldsymbol\mu$, the vector of log relative risks averaged across all health outcomes. Notice that in Figure \ref{relative_risks}a, the map showing $\boldsymbol\phi^\star_{911}$, the majority of the high risk area is concentrated in the city center. This is in line with the temperature measurements depicted in Figure \ref{fig:temp}, which shows a concentration of higher temperatures in the middle of Houston. Additionally, the area of highest concentration occurs in a downtown location with several parks and other walkable destinations, which may be a potential explanation for why heat-related 911 calls occur with relatively high frequency in this area.

There is a somewhat surprising area of extremely high relative risk for 911 calls in the northern part of the city; however, inspection of the underlying geography reveals that much of this area is covered by an airport, resulting in extremely low population levels (fewer than 25 people per square kilometer) yet a relatively large incidence of heat-related 911 calls (4, 6, and 7 phone calls in each of the three affected grid cells, respectively). Another important feature of the 911 call map is that the range for $\boldsymbol\phi^\star_{911}$ is much larger than the range for either $\boldsymbol\phi^\star_{\text{Mort}}$ or $\boldsymbol\mu$ and that far more of the $\boldsymbol\phi^\star_{911}$ values reach into the upper end of the distribution, with \textcolor{blue}{7.4} percent of $\boldsymbol\phi^\star_{911}$ values greater than 1, compared to just \textcolor{blue}{1.2} percent of the elements of $\boldsymbol\phi^\star_{\text{Mort}}$ greater than 1 and \textcolor{blue}{less than 1} percent of the elements of $\boldsymbol\mu$ greater than 1. This is likely due to sparsity of data: if more heat-related 911 calls were observed, the associated locations could potentially be more diffuse than those currently observed, leading to lower relative risk scores. Notice also that the credible interval widths (see Figure \ref{relative_risks}b), unsurprisingly, are largest where no 911 calls were observed and estimation of $\phi^\star_{911,k}$ was dependent entirely on spatial correlation.
